Calculate cloud cover of scenes

### 2021-02-16 analysis/test/cloud-cover.Rmd
new raster CRS notation

# Calculate cloud cover
cloud_scenes =
  cloud_mosaic %>%
  map(~ st_read(., quiet=TRUE)) %>%
  map(~ st_set_crs(., "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")) %>%
  map(~ st_intersection(st_buffer(., 0), aoi)) %>%
  map(possibly(~ st_union(.), NA)) %>%
  map(possibly(~ st_area(.), NA)) %>%
  map_dbl(possibly(~ sum(.), NA)) %>%
  map_dbl(possibly(~ ./aoi_area, NA))

ext_scenes =
  records %>%
  map(~ dplyr::select(., footprint)) %>%
  map_depth(2, ~ st_as_sfc(.)) %>%
  map_depth(2, ~ st_set_crs(., "+proj=longlat +datum=WGS84 +no_defs ")) %>%
  map_depth(2, ~ st_transform(., "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs")) %>%
  set_names(date_scenes)
```

>>>>

# Calculate cloud cover
cloud_scenes =
  cloud_mosaic %>%
  map(~ st_read(., quiet=TRUE)) %>%
  map(~ st_set_crs(., 25830)) %>%
  map(~ st_intersection(st_buffer(., 0), aoi)) %>%
  map(possibly(~ st_union(.), NA)) %>%
  map(possibly(~ st_area(.), NA)) %>%
  map_dbl(possibly(~ sum(.), NA)) %>%
  map_dbl(possibly(~ ./aoi_area, NA))

ext_scenes =
  records %>%
  map(~ dplyr::select(., footprint)) %>%
  map_depth(2, ~ st_as_sfc(.)) %>%
  map_depth(2, ~ st_set_crs(., 4326)) %>%
  map_depth(2, ~ st_transform(., 32630)) %>%
  set_names(date_scenes)
```
